Comprehensive optical and data management infrastructure for high-throughput light sheet microscopy of whole mouse brains

### 2015-02-16 latex-style-files-spie-manuscript/manuscript_Leo.tex
- coordinate vs cummulative adjectives and their commas :/ - other thingies

\subsection{Theoretical considerations}
\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{origin.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:origin} Optical characterisation. (A) Exemplary lateral and axial intensity profiles of sub-resolution beads and fits to Gaussian. (B) For each unit 10 bead profiles were fitted in all three dimensions and their FWHM was averaged. (C) The signal to noise ratio.} 
\end{figure}

@@

@@

For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?). The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit widths on the camera (Fig. \ref{fig:origin},B). The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively. The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig. \ref{fig:origin},C).

@@

\listoffigures
%pannel1: optical pathway, drawing images from chamber, sample mirror photos
%pannel2: software scheme
%panel3: hardware connection scheme
%panel4: data pipeline, graph data amount/time
%panel5: experiment pipeline
%panel6: images, tomos

\listoftables

@@

The fluorescent beads (\textsl{company size etc.}) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS). The low melting point agarose (A-4018, Sigma-Aldrich?) was dissolved at $40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip. The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}. The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from 0.25 units to 100 confocal units corresponding to slit widths changing from $0.175 \micro m-70 \micro m$ in the sample space. For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ (eg. Fig. \ref{fig:origin},A) throughout the depth of the image stack. After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths. The SNR was calculated according to $\text{SNR} = \nicefrac{y_0 + A}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits.

>>>>

\subsection{Theoretical considerations}

@@

\begin{figure}
   \begin{center}
   \begin{tabular}{c}
   \includegraphics[width=\textwidth]{origin.eps}
   \end{tabular}
   \end{center}
   \caption{\label{fig:origin} Optical characterisation. (A) Exemplary lateral and axial intensity profiles of sub-resolution beads and fits to Gaussian. (B) For each unit 10 bead profiles were fitted in all three dimensions and their FWHM was averaged. (C) The signal to noise ratio.} 
\end{figure}

@@

For quantitative analysis of spatial resolution and the signal to noise ratio (SNR) we acquired image stacks of subresolution sized fluorescent beads (500nm diameter?, from which company?). The spatial resolution, in agreement with previous findings\cite{Wilson1987,Cox2004}, is not affected by the confocal slit width on the camera (Fig. \ref{fig:origin},B). The lateral and axial FWHMs averaged to $(1.00\pm0.04) \micro m$ and $(8.13\pm0.14) \micro m$ respectively. The experimentally determined lateral FWHM is larger than the theoretically expected value by a factor of three and this increase is most likely due to The SNR increases with increasing slit width up to a maximum at a slit width of $7 \micro m$ corresponding to 10 confocal units (Fig. \ref{fig:origin},C).

@@

%\listoffigures
%pannel1: optical pathway, drawing images from chamber, sample mirror photos
%pannel2: software scheme
%panel3: hardware connection scheme
%panel4: data pipeline, graph data amount/time
%panel5: experiment pipeline
%panel6: images, tomos

%\listoftables

@@

\subsubsection{Sample preparation for optical characterisation}
The fluorescent beads (\textsl{company size etc.}) used for quantitative analysis of spatial resolution and the signal to noise ratio (SNR) were embedded in low- melting point agarose (2\% agarose in 64\%TDE in PBS). The low melting point agarose (A-4018, Sigma-Aldrich?) was dissolved at $40 \degree$ C then mixed with a diluted bead solution and left to polymerise over night on a coverslip. The coverslip was then mounted inside the sample chamber as described in section \ref{sec:mounting}. The embedded sub-diffraction fluorescent beads were imaged with varying confocal slit widths ranging from 0.25 units to 100 confocal units corresponding to slit widths changing from $0.175 \micro m-70 \micro m$ in the sample space. For each slit width one stack of $200\micro m$ depth ($1 \micro m$ step size) was acquired and the one dimensional PSF in the lateral and axial directions were extracted manually with FIJI/ImageJ (eg. Fig. \ref{fig:origin},A) throughout the depth of the image stack. After fitting the lateral and axial profiles with Gaussian curves, the lateral and axial FWHM were averaged (n=10 data points) for different slit widths. The SNR was calculated according to $\text{SNR} = \nicefrac{y_0 + A}{y_0}$ where $y_0$ and $A$ are the offset and amplitude of the Gaussian fits.
